---
title: "simpson_contract"
format: html
editor: visual
---

# Contract
Function: simpson_index.R

Inputs:
- each_spec = a vector containing the number of individuals in each species
- all_spec = the number of individuals in all species. should be the sum 
  of each_spec
  
Operations
- the function simpson_index.R calculates the Simpson's Biodiversity Index
  using the following equation:
  
  from 1 to length(each_spec):
  sum((each_species[i]/all_spec)^2)
  
Outputs:
- result of the Simpson Index calculation
  
# Testing simpson_index.R
```{r}
#load packages
library(here)
source(here("R/simpson_index.R"))
```


```{r}
#generate data
spec = c('Lion', 'Tiger', 'Bear', 'Penguin', 'Axolotyl')
sample_spec = as.factor(sample(spec, 1000, replace=TRUE))
char_spec = as.character(summary(sample_spec))
each_spec = as.numeric(char_spec)
summary(sample_spec)
```

```{r}
#run the function
D = simpson_index(each_spec, sum(each_spec))
D
```
```{r}
cat(sprintf("Simpson's Index = %3.1f", D))
```



